On the discovery of K-enhanced and Mg-depleted stars throughout the Milky Way\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}

### 2018-06-04 article/msculled.tex
foo
m,ef'
ascii, very minor punctuation corrections.

\subsection{Follow-up observations with Magellan/MIKE}
We acquired high-resolution spectra of three of our candidates as ancillary targets to an existing observing campaign. The three targets (J075043.12+204658.0, J091825.49+172114.5, and J120032.60+024438.2) were selected based on their observability from Las Campanas Observatory, and we used the Magellan Inamori Kyocera Echelle (MIKE) spectrograph on the Magellan Clay telescope \citep{shectman2003magellan,bernstein2003mike}. Exposure times were calculated to achieve a S/N of 30 per pixel at 450\,nm, sufficient to verify the K-enriched and Mg-poor nature of these stars. We reduced the data using the \texttt{CarPy} package \citep{kelson2003}. We used smoothing spline functions to continuum-normalize individual echelle orders, before combining them to produce a continuum-normalized spectrum that is contiguous from 350\,nm to 950\,nm. With the stellar parameters from \lamost, we calculated [K/Fe] and [Mg/Fe] abundances from individual atomic lines by measuring equivalent widths with Gaussian absorption profiles \citep{castelli2004,sneden,casey2014}. From the Magellan/MIKE spectra we confirmed that the K lines in these candidates were unaffected by telluric contamination. The estimated abundances from Magellan/MIKE spectra are consistent (within the uncertainties) of our initial abundance determinations from \lamost\ (Figure \ref{KvsMg}), and are presented in Table \ref{data:magellan}. Additional atomic line abundances are included in Table \ref{data:atomiclines} in the Appendix.
\begin{table}[H]
\centering
\caption{Summary of line abundances measured from Magellan/MIKE follow-up spectra.}
\label{data:magellan}
\begin{tabular}{lcccc}
\multicolumn{5}{c}{J075043.12+204658.0} \\
\hline
Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
\hline
\ion{Mg}{I} & 5 & 7.45 & $+$0.32 & 0.10 \\
\ion{K}{I}  & 2 & 5.33 & $+$0.77 & 0.07 \\
\hline
\\
\multicolumn{5}{c}{J091825.48+172114.5} \\
\hline
Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
\hline
\ion{Mg}{I} & 5 & 6.34 & $+$0.29 & 0.08 \\
\ion{K}{I}  & 2 & 6.28 & $+$0.85 & 0.11 \\
\hline
\\
\multicolumn{5}{c}{J120032.60+024438.2} \\
\hline
Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
\hline
\ion{Mg}{I} & 6 & 6.96 & $-$0.03 & 0.10 \\
\ion{K}{I}  & 2 & 4.96 & $+$1.22 & 0.31 \\
\hline
\end{tabular}
\end{table}

@@

\subsection{Detailed chemical abundances}
In this section, we describe the abundance trends evident from the \lamost\ and Magellan/MIKE spectra and compare with stars identified as anomalous regarding their [Mg/Fe] and [K/Fe] abundances in other studies. Abundances as well as several physical and observational parameters are available for all candidate stars online, with a 10-star sample shown in Table \ref{data:lamost}

@@

Species & $\lambda$ & $\chi$ & $\log{gf}$ & E.W. & $\log_\epsilon(\textrm{X})$ & E.W. & $\log_\epsilon(\textrm{X})$ & E.W. & $\log_\epsilon(\textrm{X})$ \\
& $({\textrm \AA})$ & $(\textrm{eV})$ & & $(\textrm{m\AA})$ & & $(\textrm{m\AA})$ & & $(\textrm{m\AA})$ \\
\hline
\ion{Mg}{I} & 4057.51 & 4.346 & $-$0.890 & 208.5 & 7.71 & 154.4 & 6.66 & 167.6 & 6.95 \\
\ion{Mg}{I} & 4167.27 & 4.346 & $-$0.710 & 231.1 & 7.11 & 123.9 & 6.27 & 192.9 & 6.69 \\
\ion{Mg}{I} & 4571.10 &   0.0 & $-$5.623 & 208.4 & 7.71 & 154.4 & 6.66 & 167.6 & 6.95 \\
\ion{Mg}{I} & 4571.10 &   0.0 & $-$5.688 & 129.7 & 7.39 & 142.1 & 7.03 &  76.4 & 7.18 \\
\ion{Mg}{I} & 4702.99 & 4.330 & $-$0.380 & 231.1 & 7.11 & 123.9 & 6.27 & 192.9 & 6.69 \\
\ion{Mg}{I} & 4730.04 & 4.340 & $-$2.389 & 129.7 & 7.39 & 142.1 & 7.03 &  76.4 & 7.18 \\
\ion{Mg}{I} & 5528.41 & 4.340 & $-$0.498 &  80.0 & 7.68 & 175.9 & 6.65 & 115.0 & 7.09 \\
\ion{Mg}{I} & 5711.09 & 4.345 & $-$1.729 & 129.7 & 7.39 & 142.1 & 7.03 &  76.4 & 7.18 \\
\ion{Mg}{I} & 5711.09 & 4.340 & $-$1.724 & 129.3 & 7.38 & 165.1 &  6.4 & 204.5 & 6.91 \\
\ion{Mg}{I} & 6318.72 & 5.108 & $-$1.945 &  80.0 & 7.68 & 175.9 & 6.65 & 115.0 & 7.09 \\
\ion{K}{I}  & 7664.90 &   0.0 & $+$0.135 & 257.8 & 5.41 &  85.6 & 6.79 & 200.7 & 4.80 \\
\ion{K}{I}  & 7698.96 &   0.0 & $-$0.168 & 202.6 & 5.25 & 379.8 & 5.76 & 201.7 & 5.11 \\
\hline
\end{tabular}
\end{table*}

>>>>

\subsection{Follow-up observations with Magellan/MIKE}
We acquired high-resolution spectra of three of our candidates as ancillary targets to an existing observing campaign. The three targets (J075043.12+204658.0, J091825.49+172114.5, and J120032.60+024438.2) were selected based on their observability from Las Campanas Observatory, and we used the Magellan Inamori Kyocera Echelle (MIKE) spectrograph on the Magellan Clay telescope \citep{shectman2003magellan,bernstein2003mike}. Exposure times were calculated to achieve a S/N of 30 per pixel at 450\,nm, sufficient to verify the K-enriched and Mg-poor nature of these stars. We reduced the data using the \texttt{CarPy} package \citep{kelson2003}. We used smoothing spline functions to continuum-normalize individual echelle orders, before combining them to produce a continuum-normalized spectrum that is contiguous from 350\,nm to 950\,nm. With the stellar parameters from \lamost, we calculated [K/Fe] and [Mg/Fe] abundances from individual atomic lines by measuring equivalent widths with Gaussian absorption profiles \citep{castelli2004,sneden,casey2014}. From the Magellan/MIKE spectra we confirmed that the K lines in these candidates were unaffected by telluric contamination. The estimated abundances from Magellan/MIKE spectra are consistent (within the uncertainties) of our initial abundance determinations from \lamost\ (Figure \ref{KvsMg}), and are presented in Table \ref{data:magellan}. Additional atomic line abundances are included in Table \ref{data:atomiclines} in the Appendix.
\begin{table}
\centering
\caption{Summary of line abundances measured from Magellan/MIKE follow-up spectra.}
\label{data:magellan}
\begin{tabular}{lcccc}
\multicolumn{5}{c}{J075043.12+204658.0} \\
\hline
Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
\hline
\ion{Mg}{I} & 3 & 7.39 & $+$0.34 & 0.13 \\
\ion{K}{I}  & 2 & 5.33 & $+$0.85 & 0.07 \\
\hline
\\
\multicolumn{5}{c}{J091825.48+172114.5} \\
\hline
Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
\hline
\ion{Mg}{I} & 5 & 6.56 & $-$0.05 & 0.08 \\
\ion{K}{I}  & 2 & 5.32 & $+$1.28 & 0.31 \\
\hline
\\
\multicolumn{5}{c}{J120032.60+024438.2} \\
\hline
Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
\hline
\ion{Mg}{I} & 4 & 6.96 & $+$0.30 & 0.09 \\
\ion{K}{I}  & 2 & 4.96 & $+$0.86 & 0.11 \\
\hline
\end{tabular}
\end{table}

@@

\subsection{Detailed chemical abundances}
In this section, we describe the abundance trends evident from the \lamost\ and Magellan/MIKE spectra and compare with stars identified as anomalous regarding their [Mg/Fe] and [K/Fe] abundances in other studies. Abundances as well as several physical and observational parameters are available for all candidate stars online, with a 10-star sample shown in Table \ref{data:lamost}.

@@

Species & $\lambda$ & $\chi$ & $\log{gf}$ & E.W. & $\log_\epsilon(\textrm{X})$ & E.W. & $\log_\epsilon(\textrm{X})$ & E.W. & $\log_\epsilon(\textrm{X})$ \\
& $({\textrm \AA})$ & $(\textrm{eV})$ & & $(\textrm{m\AA})$ & & $(\textrm{m\AA})$ & & $(\textrm{m\AA})$ \\
\hline
\ion{Mg}{1} & 4057.51 & 4.35 & $-$0.890 &        &       & 154.39 & 6.66 &        &      \\
\ion{Mg}{1} & 4167.27 & 4.35 & $-$0.710 &        &       & 123.88 & 6.27 &        &      \\
\ion{Mg}{1} & 4702.99 & 4.33 & $-$0.380 & 231.15 &  7.11 & 165.09 & 6.41 & 192.99 & 6.69 \\
\ion{Mg}{1} & 4730.04 & 4.34 & $-$2.389 &        &       &        &      &  76.41 & 7.18 \\
\ion{Mg}{1} & 5528.41 & 4.34 & $-$0.498 &        &       & 175.99 & 6.65 & 204.58 & 6.91 \\
\ion{Mg}{1} & 5711.09 & 4.34 & $-$1.724 & 129.32 &  7.38 &  85.64 & 6.80 & 115.01 & 7.09 \\
\ion{Mg}{1} & 6318.72 & 5.11 & $-$1.945 &  80.02 &  7.68 &        &      &        &      \\
\ion{K}{1}  & 7664.90 &  0.0 & $+$0.135 & 257.85 &  5.41 & 379.79 & 5.76 & 200.77 & 4.80 \\
\ion{K}{1}  & 7698.96 &  0.0 & $-$0.168 & 202.69 &  5.25 & 155.23 & 4.88 & 201.79 & 5.11 \\
\hline
\end{tabular}
\end{table*}
